A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-23 tex/body.tex
more

To reduce the number of unique literals considered by the calculus, we
compute a normal form for literals as a preprocessing step. In particular, we
replace $u \teq t$ by $t \teq u$ if $t$ is smaller than $u$ with respect to a term
ordering, replace $\smash{\const{C}_{\negvthinspace j}( \vec t \,) \teq
\const{C}_{\negvthinspace\jPrime}( \vec u )}$ with $\bot$ when $j \neq \jPrime$,
replace all selector terms of the form $\smash{\const{s}^{\,k}_{\negvthinspace j}(
\const{C}_{\negvthinspace j}(t_1,\ldots,t_n) )}$ by $t_k$, and replace
occurrences of discriminators $\smash{\const{d}_{\negvthinspace j}(
\const{C}_{\negvthinspace\jPrime}( \vec t \,) )}$ by $\top$ or $\bot$
based on whether $j = \jPrime$.

>>>>

To reduce the number of unique literals considered by the calculus, we
compute a normal form for literals as a preprocessing step. In particular, we
replace $u \teq t$ by $t \teq u$ if $t$ is smaller than $u$ with respect to some term
ordering, replace $\smash{\const{C}_{\negvthinspace j}( \vec t \,) \teq
\const{C}_{\negvthinspace\jPrime}( \vec u )}$ with $\bot$ when $j \neq \jPrime$,
replace all selector terms of the form $\smash{\const{s}^{\,k}_{\negvthinspace j}(
\const{C}_{\negvthinspace j}(t_1,\ldots,t_n) )}$ by $t_k$, and replace
occurrences of discriminators $\smash{\const{d}_{\negvthinspace j}(
\const{C}_{\negvthinspace\jPrime}( \vec t \,) )}$ by $\top$ or $\bot$
based on whether $j = \jPrime$.
